---
title: "Editathon data review"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, message=FALSE, warning=FALSE}
library(readr)
library(dplyr)
library(stringr)
library(tidyr)
library(ggplot2)
library(forcats)
```

Read in survey data

```{r, message=FALSE}
# Load edit-a-thon qualtrics data ####
raw <- read_csv('../data/WikiProject_hackathon_qualtrics.csv') # Survey responses
key <- read_csv('../data/questionKey.csv') # Question key
```

Get the text of a set of questions

```{r}
qq <- "Q8"

key %>%
  dplyr::filter(str_detect(Raw, qq)) %>%
  pull(2)
```

## Using material 

What percent of respondants used the tutorial materials provided by wikiproject LO?

```{r}
table(raw$Q6)
```

> 14 out of 15 people used the tutorial materials provided

How many people reviewed each of the types of tutorial materials?

```{r, warning=FALSE}
raw %>%
  dplyr::select(contains("Q7_")) %>% # pull out q7 answers
  dplyr::select(-contains("TEXT")) %>% # not free text response
  gather(question, material) %>% # reshape
  group_by(question) %>% 
  filter(!is.na(material)) %>% # only positive responses
  summarise(n_used = n()) %>% # count
  left_join(key, by = c("question" = "Raw")) %>% # add names
  mutate(Key = purrr::map_chr(.x = Key, ~stringr::str_sub(.x, start = 47))) %>% # shorten
  arrange(desc(n_used)) %>% dplyr::select(Key, n_used) # sort
```

What are the other materials used? 

```{r}
raw %>%
  dplyr::select(Q7_9_TEXT) %>%
  dplyr::filter(!is.na(Q7_9_TEXT))
```

> How to tag articles with the wiki project, tutorial - adding citations

## Utility of material

How useful were each of the types of material? (Q8_)

```{r}
utility_data <- raw %>%
  dplyr::select(contains("Q8_")) %>% # pull out q8 answers
  gather(question, utility) %>% # reshape
  group_by(question, utility) %>% 
  summarise(n_utility = n()) %>%
  filter(!is.na(utility)) %>% # take out NAs
  left_join(key, by = c("question" = "Raw")) %>% # add names
  ungroup() %>% dplyr::select(-question) %>%
  mutate(Key = purrr::map_chr(.x = Key, ~stringr::str_sub(.x, start = 12))) %>% # shorten
  arrange(Key, desc(n_utility))
  # spread(utility, n_utility) %>% View()
```

```{r}
utility_levels <-  c("Extremely useful", "Very useful", "Moderately useful",
    "Slightly useful", "Not at all useful", "Not applicable/ Did not use")

utility_data <- utility_data %>%
  mutate(utility_fct = forcats::as_factor(utility, utility_levels))
```

```{r}
utility_data %>%
  ggplot(aes(x = utility_fct, y = n_utility)) +
  geom_bar(stat = "identity", position = "dodge", 
           aes(fill = utility_fct), col = "black") +
  theme(axis.text.x = element_text(angle = 60, hjust = 1)) +
  xlab(element_blank()) + facet_wrap(vars(Key), ncol = 2) + 
  coord_flip() + theme_bw() +
  scale_fill_viridis_d() +
  theme(legend.position = "none") + ylab(element_blank())
```


```{r, echo=FALSE}
pdf("../figures/utility_of_materials1.pdf", width = 5.5, height = 4)
utility_data %>%
  ggplot(aes(x = utility_fct, y = n_utility)) +
  geom_bar(stat = "identity", position = "dodge", 
           aes(fill = utility_fct), col = "black") +
  theme(axis.text.x = element_text(angle = 60, hjust = 1)) +
  xlab(element_blank()) + facet_wrap(vars(Key), ncol = 2) + 
  coord_flip() + theme_bw() +
  scale_fill_viridis_d() +
  theme(legend.position = "none") + ylab(element_blank())
dev.off()
```

Stacked bar plot

```{r}
utility_data %>%
  ggplot(aes(x = Key, y = n_utility)) +
  geom_bar(stat = "identity", 
           aes(fill = utility_fct), col = "black") +
  # theme(axis.text.x = element_text(angle = 60, hjust = 1)) +
  coord_flip() + theme_bw() +
  scale_fill_viridis_d() +
  theme(legend.position = "bottom", 
        legend.text = element_text(size = 7),
          legend.title=element_blank()) +
  xlab(element_blank()) + ylab(element_blank())
```

```{r, echo = FALSE}
pdf("../figures/utility_of_materials2.pdf", width = 6, height = 3)
utility_data %>%
  ggplot(aes(x = Key, y = n_utility)) +
  geom_bar(stat = "identity", 
           aes(fill = utility_fct), col = "black") +
  # theme(axis.text.x = element_text(angle = 60, hjust = 1)) +
  coord_flip() + theme_bw() +
  scale_fill_viridis_d() +
  theme(legend.position = "bottom", 
        legend.text = element_text(size = 7),
          legend.title=element_blank()) +
  xlab(element_blank()) + ylab(element_blank())
dev.off()
```

## Other suggestions and feedback about material

Q9

```{r}
raw %>%
  dplyr::select(Q9) %>%
  filter(!is.na(Q9)) %>% pull(Q9)
```

> Video tutorial, more centralized location, wikipedia's citation template
